### 2017-06-09 Bright_Stars/LaTeX/preprint.tex
more of today's updates

% added by George
%\usepackage{wrapfig}

@@

% WATERMARKS
%\usepackage{draftwatermark}
%\SetWatermarkText{Confidential}
%\SetWatermarkScale{4}

@@

@@

@@

The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers. Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig 3. \textbf{[Insert Fig. 2]}. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.

@@

@@

\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Daniel Calto, M'hamed Aisati, Sherif El Shamy, and Holly J. Falk-Krzesinski from Elsevier for their support of this collaborative effort.

>>>>

% added by George
%\usepackage{wrapfig}
\usepackage{subcaption}

@@

% WATERMARKS
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{3}

@@

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}}
\vspace{2 mm}
\caption{
{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The unique identifier for each therapeutic is an FDA assigned NDA or BLA number. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column.}
%\begin{flushleft}  
%\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
\end{tabular}
}
\vspace{2.5 mm}
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods). Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid). Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field} 
\label{table2}
\end{adjustwidth}
\end{table}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{citing_pmid.png}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{cited_sid.png}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.  \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
\end{adjustwidth}
\end{figure}

The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers. Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig 2. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.  \textbf{[Insert Fig. 2]}.

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1.3}{
\includegraphics[scale=0.1]{cy_core14_v2csv_5.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\includegraphics[scale=0.1]{proj_percent.png}
\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods). 19,104 unique project numbers were identified as sources of support for publications in all five networks. Of these, 112 projects were common to all five networks. Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research. For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals). A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
\label{fig3}
\end{adjustwidth}
\end{figure}

@@

\section*{Acknowledgments} We thank Sandeep Somaiya from NETE as well as Holly J. Falk-Krzesinski from Elsevier for their support of this collaborative effort.
